Properties of winning Iterated Prisoner's Dilemma strategies.

### 2020-03-30 paper/main.tex
Revise abstract

\begin{abstract}
From the celebrated performance of Tit for Tat, to the
introduction of the zero-determinant strategies, to the use of sophisticated
structures such as neural networks, the literature has been exploring the
performance of Iterated Prisoner's Dilemma strategies for decades. The results of the literature,
however, have been relying on a small number of somewhat arbitrarily selected
strategies in a very small number of tournaments,
casting doubt on the generalizability of results from statistical perspective.
This manuscript evaluates \numberofstrategies strategies in 45686
tournaments, presents the top performing strategies, and analyzes their
salient features. The results imply that there is not yet a single
strategy that performs well in every Iterated Prisoner's Dilemma interaction.
There are several properties, however, that heavily influence the best performing
strategies, these are: be nice, be provocable and contrite, be a little envious, be clever
and adapt to the environment.
\end{abstract}

>>>>

\begin{abstract}
Researchers have explored the performance of Iterated Prisoner's Dilemma strategies
for decades: from the celebrated performance of Tit for Tat, to the
introduction of the zero-determinant strategies, to the use of sophisticated learning
structures such as neural networks, many new strategies have been introduced and tested
in a variety of tournaments and population dynamics. Typical results in the literature,
however, rely on performance against a small number of somewhat arbitrarily selected
strategies in a very small number of tournaments, casting doubt on the generalizability
of conclusions. We analyze a large collection of \numberofstrategies
strategies in \numberofalltournaments tournaments, present the top performing strategies across multiple
tournament types, and distill their salient features. The results show that there is not yet a single
strategy that performs well in diverse Iterated Prisoner's Dilemma scenarios.
Nevertheless there are several properties that heavily influence the best performing
strategies, refining the properties described by R. Axelrod in light of
recent and more diverse opponent populations. These are: be nice, be provocable and contrite,
be a little envious, be clever, and adapt to the environment, which includes the parameters
of the tournament (e.g. noise) and the population of opponents. More precisely,
we find that strategies perform best when their probability of cooperation
matches the total tournament population's aggregate cooperation probabilities,
or a proportion thereof in the case of noisy and probabilistically ending tournaments,
and that the manner in which a strategy achieves the ideal cooperation rate is crucial.
\end{abstract}
